### 2016-03-10 paper4.tex
Derotated some figures, and put all table captions above the table.
Made all references unique to its own paper/chapter.

\section{Introduction}
\label{sec:intro}
Several groups \citep[e.g.][]{Wittenmyer2006, Fischer2009, Pepe2011} have used the radial velocity method to search for planets around nearby stars for well over a decade, and have collectively uncovered several hundred planets to date. Close binary stars are usually cut from the star sample because they complicate the detection method \citep[e.g.][]{Bergmann2015}, and because they have long been suspected to inhibit planet formation by quickly destroying \citep{Kraus2012} or depleting \citep{Harris2012} the planet-forming disk.

@@

Here, we use all of our spectra of $\psi^1$ Dra A to search directly for the spectral lines of the companion and measure the system mass ratio. We describe the observations and data reduction in Section \ref{sec:obs}, and the method we use to search for the companion in Section \ref{sec:method}. Finally, we estimate the mass-ratio of the system and give the parameters for the companion in Section \ref{sec:orbit}.

\section{Observations and Data Reduction}
\label{sec:obs}
All data were taken at the 2.7 m Harlan J. Smith Telescope at McDonald observatory using the 2dcoud\'e \'echelle spectrograph \citep{TS23} at a resolving power $R\equiv \frac{\lambda}{\Delta \lambda} = 60000$. The starlight was filtered through a temperature-stabilized $I_2$ cell to imprint many sharp absorption lines on each spectrum to use for both a precise velocity metric \citep{Butler1996} and to model the instrument profile \citep{Endl2000}. The raw CCD data were reduced with standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and include steps for overscan trimming, bad--pixel processing, bias--frame subtraction, scattered--light removal, flat--field division, order extraction, and wavelength solution fitting using a Th--Ar calibration lamp spectrum. Particularly strong cosmic--ray hits were removed manually by interpolating across nearby pixels.

We used the \emph{Austral} code \citep{Endl2000} to measure the differential radial velocity of $\psi^1$ Dra A at each observation by comparing each spectrum to a high signal-to-noise ratio template spectrum of the same star. We provide the raw velocity measurements in Table \ref{tab:rv_data}, as well as the velocities shifted into the system velocity rest frame. The velocity shift necessary to convert from the differential radial velocities to that frame is found in Section \ref{sec:orbit}. Table \ref{tab:rv_data} also gives the measurements of the companion radial velocity (described in the next section).

@@

    \caption{The velocities in the `raw' columns are our actual measurements. Those in the `shifted' columns are shifted into the system velocity rest frame using the results of the orbital fit described in Section \ref{sec:orbit}.} \\
  \label{tab:rv_data}

@@

\section{Companion Search}
\label{sec:method}

@@

We normalize each CCF by subtracting a quadratic function that we fit well away from the peak, and then dividing by the height of the CCF at $v=0$ (the peak). The average of the shifted CCFs is a close estimate for the cross-correlation function of the M-star template with the F5 primary star, since the contribution from the companion is diluted by shifting the CCFs to the primary star rest frame. We remove the contribution from the primary star by subtracting the average from each CCF. The result is a series of residual cross-correlation functions that are estimates for the CCF of the companion spectrum against the 4400 K model spectrum template, with significant noise. We show the residual CCFs in Figure \ref{fig:resids}; the trace of the companion star is easily visible as the dark curve near the top middle. We are unable to recover the companion signal at early dates when the two stars were close to one another in velocity space.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Resid_CCFs.pdf}
  \caption{Cross-correlation functions of a 4400 K model spectrum template with the data, after subtraction of the average CCF. The dark curve in the top middle is the signal of the companion star.}
  \label{fig:resids}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Typical_CCF.pdf}
  \caption{An example of a typical residual cross-correlation function. The dominant peak denotes the template match of the 4400 K template with the companion to $\psi^1$ Draconis A. The velocities are in the approximate rest frame of the primary star (see text for details), and the centroid and FWHM are given as vertical dotted lines.}
  \label{fig:ccf_typical}
\end{figure}

We measure the radial velocity of the companion at each epoch by finding the maximum and full-width-half-maximum (FWHM) of the residual CCF. On the basis of Figure \ref{fig:resids}, we use only the portion of the CCFs with $-50 < v < 10\ \mathrm{km\ s}^{-1}$; we show a typical residual CCF in Figure \ref{fig:ccf_typical}. Since the CCFs were shifted to subtract the contribution from the primary star, the measured velocities ($v_{m, 2}$) are related to the true barycentric velocities ($v_1$ and $v_2$ for the primary and secondary, respectively) and the constant shift described above ($\Delta v_2$) through

\begin{equation}
v_{m, 2}(t) = v_2(t) - v_1(t) + \Delta v_2
\label{eqn:vel}
\end{equation}

We give the measured companion velocities in Table \ref{tab:rv_data} (column 5). We additionally provide the velocities in the system velocity rest--frame ($v_2$) by using Equation \ref{eqn:vel} and the results of the analysis described below. The uncertainties given in Table \ref{tab:rv_data} are determined from the CCF peak width and the scaling factor ($f$) derived below. The shifted primary and secondary velocities given in Table \ref{tab:rv_data} are for the reader's convenience since they are in the same reference frame; we use the raw measurements in the orbital fit.

\section{Orbital Fit}
\label{sec:orbit}

@@

The companion radial velocities are measured relative to the primary star plus a small velocity shift ($\Delta v_2$) caused by slight inaccuracies in the vacuum--to--air wavelength conversion in the model spectrum and spectrograph wavelength drift throughout the night. Finally, the CCF peak full-width at half maximum vastly over-estimates the velocity uncertainty and so we fit a scale factor ($f$) to apply to the companion velocity uncertainties. The uncertainties given in Table \ref{tab:rv_data} are already scaled by that factor. The full log-likelihood function ($\mathcal{L}$) is then given by:

@@

We use the affine invariant sampler provided in the emcee code \citep{emcee} to perform a Markov Chain Monte Carlo (MCMC) fit to all of the parameters described above. We use flat priors in all variables except for the rv--jitter and companion rv uncertainty scale factors ($\sigma_J$ and $f$, respectively), for which we use log-uniform priors to allow for a large range of values.  We give the median value and uncertainty for each parameter in Table \ref{tab:orbit}. The uncertainties are estimated from the posterior probability distribution samples such that the lower and upper bounds give the 16th and 84th percentile (i.e. they are $1\sigma$ credibility intervals). We plot the best-fit orbit with the data in Figure \ref{fig:orbit}, with the uncertainties on the companion velocities scaled and the velocities shifted by $\Delta v_1$ and $\Delta v_2$.

Next, we calculate a series of derived quantities to characterize the companion and report them in Table \ref{tab:orbit}. The mass ratio of the system is the ratio $K_1/K_2 = 0.47$. We estimate the primary star mass by interpolating Dartmouth isochrones \citep{Dotter2008} with the `isochrones' code \citep[described in][]{Montet2015}, and using spectroscopic parameters derived in \citet{Endl2015}. The secondary mass is $M_2 = qM_1 \sim 0.70\ M_{\odot}$; assuming the same age and metallicity as the primary, the Dartmouth isochrones give an expected temperature of ${\sim}4400 $ K. That temperature is in excellent agreement with the high--contrast--imaging data, which support a companion of ${\sim}4400$ K with large uncertainty. With both the primary and secondary star mass, we calculate the orbital inclination and semimajor axis and report them in Table \ref{tab:orbit}.

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{rl}
    \hline

@@

\caption{The primary mass is derived using the spectroscopic $T_\mathrm{eff}$, $\log{g}$, and [Fe/H] and interpolating Dartmouth isochrones. The companion temperature is likewise derived from the companion mass using Dartmouth isochrones of the same metallicity.}
\label{tab:orbit}
\end{table}

@@

  \includegraphics[width=\columnwidth]{Figures/paper4_SB2_Orbit.pdf}
  \caption{Best-fit double-lined orbit for the $\psi^1$ Draconis AC subsystem. There are no measurements of the companion at early dates because they could not be reliably measured in the residual cross-correlation functions.}
  \label{fig:orbit}

@@

We use nearly 15 years of time-series spectra of the star $\psi^1$ Draconis A to search for the spectral lines of a companion identified by a large--amplitude trend in the primary--star radial velocities and later by direct imaging. We cross-correlate each spectrum against a Phoenix model spectrum of a $4400$ K star and subtract the average CCF. The residual CCFs clearly show the template match with the companion (Figure \ref{fig:resids}), and we are able to measure the companion radial velocities for most dates.

We use the radial--velocity measurements for both the primary and secondary stars to find an orbital solution for the now double-lined spectroscopic binary. The summary values of the fitted parameters are given in Table \ref{tab:orbit}. Finally, we report the mass and expected temperature of the companion as well as the orbital inclination and semi--major axis. The temperature agrees well with high--contrast imaging, validating our method.

The $\psi^1$ Draconis system is therefore a hierarchical multiple system with the component parameters given in Table \ref{tab:orbit}. $\psi^1$ Dra A and B are separated by ${\sim}680$ AU and have a mass-ratio $q = 0.82$, while A and C (the new companion) have a much closer orbit with with $a = 9.1$ AU and $q = 0.47$.

>>>>

\section{Introduction}
\label{paper4_sec:intro}
Several groups \citep[e.g.][]{Wittenmyer2006, Fischer2009, Pepe2011} have used the radial velocity method to search for planets around nearby stars for well over a decade, and have collectively uncovered several hundred planets to date. Close binary stars are usually cut from the star sample because they complicate the detection method \citep[e.g.][]{Bergmann2015}, and because they have long been suspected to inhibit planet formation by quickly destroying \citep{Kraus2012} or depleting \citep{Harris2012} the planet-forming disk.

@@

Here, we use all of our spectra of $\psi^1$ Dra A to search directly for the spectral lines of the companion and measure the system mass ratio. We describe the observations and data reduction in Section \ref{paper4_sec:obs}, and the method we use to search for the companion in Section \ref{paper4_sec:method}. Finally, we estimate the mass-ratio of the system and give the parameters for the companion in Section \ref{paper4_sec:orbit}.

\section{Observations and Data Reduction}
\label{paper4_sec:obs}
All data were taken at the 2.7 m Harlan J. Smith Telescope at McDonald observatory using the 2dcoud\'e \'echelle spectrograph \citep{TS23} at a resolving power $R\equiv \frac{\lambda}{\Delta \lambda} = 60000$. The starlight was filtered through a temperature-stabilized $I_2$ cell to imprint many sharp absorption lines on each spectrum to use for both a precise velocity metric \citep{Butler1996} and to model the instrument profile \citep{Endl2000}. The raw CCD data were reduced with standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and include steps for overscan trimming, bad--pixel processing, bias--frame subtraction, scattered--light removal, flat--field division, order extraction, and wavelength solution fitting using a Th--Ar calibration lamp spectrum. Particularly strong cosmic--ray hits were removed manually by interpolating across nearby pixels.

We used the \emph{Austral} code \citep{Endl2000} to measure the differential radial velocity of $\psi^1$ Dra A at each observation by comparing each spectrum to a high signal-to-noise ratio template spectrum of the same star. We provide the raw velocity measurements in Table \ref{paper4_tab:rv_data}, as well as the velocities shifted into the system velocity rest frame. The velocity shift necessary to convert from the differential radial velocities to that frame is found in Section \ref{paper4_sec:orbit}. Table \ref{paper4_tab:rv_data} also gives the measurements of the companion radial velocity (described in the next section).

@@

    \caption{The velocities in the `raw' columns are our actual measurements. Those in the `shifted' columns are shifted into the system velocity rest frame using the results of the orbital fit described in Section \ref{paper4_sec:orbit}.} \\
  \label{paper4_tab:rv_data}

@@

\section{Companion Search}
\label{paper4_sec:method}

@@

We normalize each CCF by subtracting a quadratic function that we fit well away from the peak, and then dividing by the height of the CCF at $v=0$ (the peak). The average of the shifted CCFs is a close estimate for the cross-correlation function of the M-star template with the F5 primary star, since the contribution from the companion is diluted by shifting the CCFs to the primary star rest frame. We remove the contribution from the primary star by subtracting the average from each CCF. The result is a series of residual cross-correlation functions that are estimates for the CCF of the companion spectrum against the 4400 K model spectrum template, with significant noise. We show the residual CCFs in Figure \ref{paper4_fig:resids}; the trace of the companion star is easily visible as the dark curve near the top middle. We are unable to recover the companion signal at early dates when the two stars were close to one another in velocity space.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Resid_CCFs.pdf}
  \caption{Cross-correlation functions of a 4400 K model spectrum template with the data, after subtraction of the average CCF. The dark curve in the top middle is the signal of the companion star.}
  \label{paper4_fig:resids}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper4_Typical_CCF.pdf}
  \caption{An example of a typical residual cross-correlation function. The dominant peak denotes the template match of the 4400 K template with the companion to $\psi^1$ Draconis A. The velocities are in the approximate rest frame of the primary star (see text for details), and the centroid and FWHM are given as vertical dotted lines.}
  \label{paper4_fig:ccf_typical}
\end{figure}

We measure the radial velocity of the companion at each epoch by finding the maximum and full-width-half-maximum (FWHM) of the residual CCF. On the basis of Figure \ref{paper4_fig:resids}, we use only the portion of the CCFs with $-50 < v < 10\ \mathrm{km\ s}^{-1}$; we show a typical residual CCF in Figure \ref{paper4_fig:ccf_typical}. Since the CCFs were shifted to subtract the contribution from the primary star, the measured velocities ($v_{m, 2}$) are related to the true barycentric velocities ($v_1$ and $v_2$ for the primary and secondary, respectively) and the constant shift described above ($\Delta v_2$) through

\begin{equation}
v_{m, 2}(t) = v_2(t) - v_1(t) + \Delta v_2
\label{paper4_eqn:vel}
\end{equation}

We give the measured companion velocities in Table \ref{paper4_tab:rv_data} (column 5). We additionally provide the velocities in the system velocity rest--frame ($v_2$) by using Equation \ref{paper4_eqn:vel} and the results of the analysis described below. The uncertainties given in Table \ref{paper4_tab:rv_data} are determined from the CCF peak width and the scaling factor ($f$) derived below. The shifted primary and secondary velocities given in Table \ref{paper4_tab:rv_data} are for the reader's convenience since they are in the same reference frame; we use the raw measurements in the orbital fit.

\section{Orbital Fit}
\label{paper4_sec:orbit}

@@

The companion radial velocities are measured relative to the primary star plus a small velocity shift ($\Delta v_2$) caused by slight inaccuracies in the vacuum--to--air wavelength conversion in the model spectrum and spectrograph wavelength drift throughout the night. Finally, the CCF peak full-width at half maximum vastly over-estimates the velocity uncertainty and so we fit a scale factor ($f$) to apply to the companion velocity uncertainties. The uncertainties given in Table \ref{paper4_tab:rv_data} are already scaled by that factor. The full log-likelihood function ($\mathcal{L}$) is then given by:

@@

We use the affine invariant sampler provided in the emcee code \citep{emcee} to perform a Markov Chain Monte Carlo (MCMC) fit to all of the parameters described above. We use flat priors in all variables except for the rv--jitter and companion rv uncertainty scale factors ($\sigma_J$ and $f$, respectively), for which we use log-uniform priors to allow for a large range of values.  We give the median value and uncertainty for each parameter in Table \ref{paper4_tab:orbit}. The uncertainties are estimated from the posterior probability distribution samples such that the lower and upper bounds give the 16th and 84th percentile (i.e. they are $1\sigma$ credibility intervals). We plot the best-fit orbit with the data in Figure \ref{paper4_fig:orbit}, with the uncertainties on the companion velocities scaled and the velocities shifted by $\Delta v_1$ and $\Delta v_2$.

Next, we calculate a series of derived quantities to characterize the companion and report them in Table \ref{paper4_tab:orbit}. The mass ratio of the system is the ratio $K_1/K_2 = 0.47$. We estimate the primary star mass by interpolating Dartmouth isochrones \citep{Dotter2008} with the `isochrones' code \citep[described in][]{Montet2015}, and using spectroscopic parameters derived in \citet{Endl2015}. The secondary mass is $M_2 = qM_1 \sim 0.70\ M_{\odot}$; assuming the same age and metallicity as the primary, the Dartmouth isochrones give an expected temperature of ${\sim}4400 $ K. That temperature is in excellent agreement with the high--contrast--imaging data, which support a companion of ${\sim}4400$ K with large uncertainty. With both the primary and secondary star mass, we calculate the orbital inclination and semimajor axis and report them in Table \ref{paper4_tab:orbit}.

\begin{table}
  \centering
\caption{The primary mass is derived using the spectroscopic $T_\mathrm{eff}$, $\log{g}$, and [Fe/H] and interpolating Dartmouth isochrones. The companion temperature is likewise derived from the companion mass using Dartmouth isochrones of the same metallicity.}
  \footnotesize
  \begin{tabular}{rl}
    \hline

@@

\label{paper4_tab:orbit}
\end{table}

@@

  \includegraphics[width=\columnwidth]{Figures/paper4_SB2_Orbit.pdf}
  \caption{Best-fit double-lined orbit for the $\psi^1$ Draconis AC subsystem. There are no measurements of the companion at early dates because they could not be reliably measured in the residual cross-correlation functions.}
  \label{paper4_fig:orbit}

@@

We use nearly 15 years of time-series spectra of the star $\psi^1$ Draconis A to search for the spectral lines of a companion identified by a large--amplitude trend in the primary--star radial velocities and later by direct imaging. We cross-correlate each spectrum against a Phoenix model spectrum of a $4400$ K star and subtract the average CCF. The residual CCFs clearly show the template match with the companion (Figure \ref{paper4_fig:resids}), and we are able to measure the companion radial velocities for most dates.

We use the radial--velocity measurements for both the primary and secondary stars to find an orbital solution for the now double-lined spectroscopic binary. The summary values of the fitted parameters are given in Table \ref{paper4_tab:orbit}. Finally, we report the mass and expected temperature of the companion as well as the orbital inclination and semi--major axis. The temperature agrees well with high--contrast imaging, validating our method.

The $\psi^1$ Draconis system is therefore a hierarchical multiple system with the component parameters given in Table \ref{paper4_tab:orbit}. $\psi^1$ Dra A and B are separated by ${\sim}680$ AU and have a mass-ratio $q = 0.82$, while A and C (the new companion) have a much closer orbit with with $a = 9.1$ AU and $q = 0.47$.
